\tool: A Multi-Mode BadUSB Device

### 2021-01-08 WOOT/Files/related_work.tex

Tian, Jing, et al.[1] have made a brief overview of the defense countermeasures over four layers attack in the article. For attacks against human-layer problems, [2],[3]raise people's awareness of social engineering,[][][4],[5],[6] prevent the data from being stolen by on-device encryption, [7],[8] provide host authentication, [8]monitor data flow to record potential malicious IO behaviors and [9],[10]block physical connections to defense. In application layer,modification over OS and driver are adapted. [11],[12],[13] harden  host system to prevent automatic execution of malicious code. GOOD USB[14] offers strict access control, with the system soliciting desired functionality from the user and blocking other functionality for a device. Ghost[15] simulates as a USB device to detect if the host has malicious code injection. In transport layer,

FirmUSB[16] and VIPER[17] check the firmware of the device to ensure its safety. Fuzzing is a method of detecting vulnerabilities by providing unexpected input to the target system and monitoring for abnormal results. Some related work,[][][18],[19],[20] ,focuses on using USB fuzzing approach to detect potential bugs in USB driver. USBFirewall[21] protects the host based on error detection of USB communication packages. In some related work, [14],[22], e. g, VM is deployed in host to interact with the USB device for malicious behavior detection. In physical layer, some related work like [23] consider anti-fingerprinting ,and some others like [24] consider data encryption on USB bus.

>>>>

There are already some defense measures against USB attacks. Since USB devices may hide their real functionality from the user. GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user before the enumeration is completed. The user needs to explicitly specify the useful functionality of the device. On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage. This restricts the device from loading only the drivers allowed by the user, but does not prevent the device from using available drivers to attack. For example, a malicious keyboard can type commands without the user's knowledge after enumeration. What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of malicious code.

IMonitor EAM\cite{IMonitor} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host. This prevents all interactions between untrusted devices and the host. But this reduces the ease of use and requires users to have a certain safety awareness. For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.

Google\cite{Googleukip} has developed a security tool for Linux systems that can prevent USB key injection attacks from malicious U disk devices by identifying suspicious keystroke speeds. This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering. This leads to a very short interval between key events.

Some composite anti-virus systems, like Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware. However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.
